Analyzing X-ray images in Python with scikit-image

### 2016-08-21 skimage_tomo.tex
Various text tweaks

    \texttt{scikit-image} is an open-source image processing toolkit for
    the Python language, that supports a large variety of file formats
    and is compatible with 2-D and 3-D images. The toolkit exposes a
    simple programming interface, corresponding to functions performing
    operations on images, and different thematic modules that group these
    functions according to their purpose, such as image restoration,
    segmentation, measurements, etc. \texttt{scikit-image} users benefit
    from the rich ecosystem of Python for science, with powerful
    visualization libraries or machine learning toolkits.
    \texttt{scikit-image} combines a gentle
    learning curve, versatile image processing capabilities, and the
    scalable performances required for the high-throughput analysis of
    X-ray imaging data.

@@

\texttt{scikit-image} has a very simple Application Programming Interface
(API), based almost only on
functions. Most functions take an image (\emph{i.e} a multi-dimensional
array) as input parameter:
\begin{lstlisting}
>>> from skimage import filters
>>> im_gaussian = filters.gaussian(im)
\end{lstlisting}

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
    \caption{\csentence{Typical image processing operations with
	\texttt{scikit-image}.} From left to right and top to bottom.
	Data are syntheric, unless stated otherwise.
	\textbf{Filtering -} Top: non-local means denoising of an image
	with a fine-grained texture, acquired by \emph{in situ}
	synchrotron microtomography during
	glass melting \citep{Gouillart2012}. Bottom: total-variation
	denoising of an image with two phases, corresponding to
	phase-separating silicate melts observed by \emph{in situ
	tomography} \citep{Bouttes2015}.
	\textbf{Feature extraction -} Top: Hubble deep field (NASA,
	public domain), blob detection using the
	Laplacian of Gaussian method. Bottom: ridge detection using the
	leading value of the Hessian matrix. 
	\textbf{Segmentation - } Top: super-pixel segmentation
	of a CT slice of the human head \citep{tomo_wikipedia}, using
	Felzenszwalb's algorithm \citep{Felzenszwalb2004}. Bottom: random
	walker segmentation (right) of noisy image (top-left corner), using
	histogram-determined markers (bottom-left corner).
	\textbf{Measures -} Top: visualization of local diameter
	(color-coded on the skeleton curve) of an
	interconnected phase (represented in violet).  Bottom: particles color-coded according
	to their extent.
\label{fig:tomo_gallery}}
\end{figure*}

@@

An easy solution consists in dividing an image into smaller images (with
or without overlap, depending on the operation), and to apply the
same operation on the different sub-images, on different cores. Creating overlapping chunks is easy with the dedicated function \texttt{view\_as\_windows} (or \texttt{view\_as\_blocks} for contiguous non-overlapping chunks):
\begin{lstlisting}[language=Python]
>>> from skimage import util, data
>>> im = data.camera()
>>> im.shape
(512, 512)
>>> # chunks of size 120 with 8-pixel overlap
>>> chunks = util.view_as_windows(im, (128, 128), step=120)
>>> chunks.shape
(4, 4, 128, 128)
\end{lstlisting}
The \texttt{joblib} module enables easy parallel processing. Looping over the different blocks, and dispatching the computation over several cores, is realized with the following syntax:  
\begin{lstlisting}
>>> from joblib import Parallel, delayed
>>> filtered_chunks = Parallel(n_jobs=4)(delayed(filters.gaussian)(chunks[i, j]) for i in range(4) for j in range(4))
\end{lstlisting}
\texttt{scikit-image} also offers experimental support for a more integrated parallel processing pipeline, thanks to the \texttt{dask} \citep{dask} module:
\begin{lstlisting}
filtered_im = util.apply_parallel(filters.gaussian, im, depth=8)
\end{lstlisting}
The size of chunks is determined automatically from the number of available cpus, or can be specified by the user.

>>>>

    \texttt{scikit-image} is an open-source image processing toolkit for
    the Python language, that supports a large variety of file formats
    and is compatible with 2-D and 3-D images. The toolkit exposes a
    simple programming interface, with thematic modules grouping
    functions according to their purpose, such as image restoration,
    segmentation, and measurements. \texttt{scikit-image} users benefit
    from the rich ecosystem of Python for science, with powerful
    visualization libraries or machine learning toolkits.
    \texttt{scikit-image} combines a gentle
    learning curve, versatile image processing capabilities, and the
    scalable performances required for the high-throughput analysis of
    X-ray imaging data.

@@

\texttt{scikit-image} has a simple Application Programming Interface
(API), based almost only on
functions. Most functions take an image (\emph{i.e} a multi-dimensional
array) as input parameter:
\begin{lstlisting}
>>> from skimage import filters
>>> im_gaussian = filters.gaussian(im)
\end{lstlisting}

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
    \caption{\csentence{Typical image processing operations with
	\texttt{scikit-image}.} From left to right and top to bottom.
	Data are synthetic, unless stated otherwise.
	\textbf{Filtering -} Top: non-local means denoising of an image
	with a fine-grained texture, acquired by \emph{in situ}
	synchrotron microtomography during
	glass melting \citep{Gouillart2012}. Bottom: total-variation
	denoising of an image with two phases, corresponding to
	phase-separating silicate melts observed by \emph{in situ
	tomography} \citep{Bouttes2015}.
	\textbf{Feature extraction -} Top: Hubble deep field (NASA,
	public domain), blob detection using the
	Laplacian of Gaussian method. Bottom: ridge detection using the
	leading value of the Hessian matrix. 
	\textbf{Segmentation - } Top: super-pixel segmentation
	of a CT slice of the human head \citep{tomo_wikipedia}, using
	Felzenszwalb's algorithm \citep{Felzenszwalb2004}. Bottom: random
	walker segmentation (right) of noisy image (top-left corner), using
	histogram-determined markers (bottom-left corner).
	\textbf{Measures -} Top: visualization of local diameter
	(color-coded on the skeleton curve) of an
	interconnected phase (represented in violet).  Bottom: particles color-coded according
	to their extent.
\label{fig:tomo_gallery}}
\end{figure*}

@@

An easy solution consists in dividing an image into smaller images (with
or without overlap, depending on the operation), and to apply the
same operation on the different sub-images, on different cores. Creating overlapping chunks is easy with the dedicated function \texttt{view\_as\_windows} (or \texttt{view\_as\_blocks} for contiguous non-overlapping chunks):
\begin{lstlisting}[language=Python]
>>> from skimage import util, data
>>> im = data.camera()
>>> im.shape
(512, 512)
>>> # chunks of size 120 with 8-pixel overlap
>>> chunks = util.view_as_windows(im, (128, 128), step=120)
>>> chunks.shape
(4, 4, 128, 128)
\end{lstlisting}
The \texttt{joblib} library enables easy parallel processing. Looping over the different blocks, and dispatching the computation over several cores, is realized with the following syntax:
\begin{lstlisting}
>>> from joblib import Parallel, delayed
>>> filtered_chunks = Parallel(n_jobs=4)(delayed(filters.gaussian)(chunks[i, j]) for i in range(4) for j in range(4))
\end{lstlisting}
\texttt{scikit-image} also offers experimental support for a more integrated parallel processing pipeline, thanks to the \texttt{dask} \citep{dask} module:
\begin{lstlisting}
filtered_im = util.apply_parallel(filters.gaussian, im, depth=8)
\end{lstlisting}
The size of chunks is determined automatically from the number of available cpus, or can be specified by the user.
